A Formal Model of Checked C

### 2023-01-12 sandp23/overview.tex
Adding all
Adding Implementation section and modifying evaluation section

%\Cref{sec:formal} provides the formalism of the different compiler components.
%Converting a C/checked-c program to \systemname is a two-step process that involves identifying unsafe/unchecked regions described in \Cref{subsec:identifyregionstosbx} followed by making the \systemname changes described in \Cref{subsec:moveregionstosbx}.  
\subsection{Running Example}
\label{subsec:identifyregionstosbx}
Here,
we use the example of a simple network server in~\lst{lst:comb} to explain changes required by the \systemname compiler.
The~\lst{lst:comb} shows the C code of the redacted version of a simple network server with~\code{server_loop} as its entry point (\entrypoint).
The server runs in a loop and calls~\code{handle_request}, which handles each network request.
The function~\code{handle_request} reads data from the socket through~\code{read_msg} and based on the first byte, either~\code{process_req1} or~\code{process_req2} will be called to handle the request.

>>>>

%\Cref{sec:formal} provides the formalism of the different compiler components.
%Converting a C/checked-c program to \systemname is a two-step process that involves identifying unsafe/unchecked regions described in \Cref{subsec:identifyregionstosbx} followed by making the \systemname changes described in \Cref{subsec:moveregionstosbx}.  
\subsection{Running Example}
\label{subsec:identifyregionstosbx}
to explain changes required by the \systemname compiler.The~\lst{lst:comb} shows the C code of the redacted version of a simple network server with~\code{server_loop} as its entry point (\entrypoint).
The server runs in a loop and calls~\code{handle_request}, which handles each network request.
The function~\code{handle_request} reads data from the socket through~\code{read_msg} and based on the first byte, either~\code{process_req1} or~\code{process_req2} will be called to handle the request.
